\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2015-01-08 proposal/sections/costs.tex
Costs

\section{Costs}
\label{sect:costs}

\note{
\begin{itemize}
\item {\em Length: 2-3 pages}
\item Rough estimation of cost in form of calculation (table(s)) + descriptive text.
\item Justification for the personnel and non-personnel costs (equipment, material, travel and other costs)
\item An Excel template is provided as supplementary material to support budgeting.
\item Personnel costs
	\begin{itemize}
	\item     Justification for the personnel to be assigned to the project (type of position(s), description of nature of work, length and extent of involvement in the project)
	\item     The application should include all persons who will be required for the proposed project (project lead, researchers, developers, advisory board, etc.). The available legal categories of employment are contracts of employment for full- or part-time employees (DV) and reimbursement for work on an hourly basis (GB). In addition, a part-time contract of employment (DV 50\%, ``studentische Mitarbeiter'') may be requested for people who have not yet completed a Master or Diploma program (Diplom) in the relevant subject.
	 \item    The justification of the requested personnel should contain:
		\begin{itemize}
		\item 	        description of type of work;
		\item 		        extent of involvement (part-time contracts are permitted).
		\end{itemize}
	\item Exact numbers of employment categories can be found on the FWF Website (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
	\end{itemize}
\item Equipment costs
	\begin{itemize}
	\item     Indicate reasons for equipment costs. The ``scientific equipment'' category includes instruments, system components, costs for the use of software required by the project and other durable goods provided the cost per item (including VAT) exceeds EUR 1,500.00.
	\end{itemize}
\item Material costs
	\begin{itemize}
	\item     This category encompasses consumables and smaller pieces of equipment where the cost per item is below EUR 1,500.00 including VAT. The calculation of requested material costs should be justified with reference to the schedule, work plan and experimental plan. Experience with previous projects should be taken into account.
	\end{itemize}
\item Travel costs
	\begin{itemize}
	\item     Funding may be requested for the costs of project-specific travel and accommodation, field work, expeditions, etc. Applicants are to provide a detailed travel (cost) plan broken down by project participant. For brief stays, the calculation of the travel and accommodation costs should be based on the federal regulations governing travel costs (RGV). The RGV rates governing Austria and abroad may be found in the FAQs on the FWF Website (\href{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}). For longer stays an appropriate and comprehensible cost plan should be prepared.
	\end{itemize}
\item Other costs
	\begin{itemize}
	\item     Independent contracts for work and services (costs for work of clearly defined scope and content assigned to individuals, provided that this is scientifically justifiable and economical)
    	\item     Costs that cannot be included under personnel, equipment, material or travel costs, such as:
		\begin{itemize}
		\item         reimbursement of costs towards or for the use of research facilities, e.g. of large-scale research facilities (project-specific 'equipment time'). Applicants should obtain and submit multiple offers;
		\item         costs for project-specific work carried out outside the applicant's research institution (e.g. for analysis work performed elsewhere, for interviews, for sample collection, for preparation of thin slices etc.). Applicants should obtain and submit multiple offers;
		\item         honoraria for test persons;
		\end{itemize}
	\end{itemize}
\end{itemize}
}

>>>>

\section{Costs}
\label{sect:costs}
\subsection{Person}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Person & Commitment & 1st Year & 2nd Year & 3rd Year & 4th Year & Sum \\ 
\hline 
Project Manager & 100\% & 54000 & • & • & • & • \\ 
\hline 
Quality Manager & 75\% & 27000 & • & • & • & • \\ 
\hline 
• & • & • & • & • & • & • \\ 
\hline 
• & • & • & • & • & • & • \\ 
\hline 
• & • & • & • & • & • & • \\ 
\hline 
• & • & • & • & • & • & • \\ 
\hline 
• & • & • & • & • & • & • \\ 
\hline 
• & • & • & • & • & • & • \\ 
\hline 
• & • & • & • & • & • & • \\ 
\hline 
• & • & • & • & • & • & • \\ 
\hline 
\end{tabular}

\subsection{Hardware}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
Item & 1st Year & 2nd Year & 3rd Year & 4th Year & Sum \\ 
\hline 
Commercial EEG Headsets & 3000 & • & • & • & • \\ 
\hline 
Medical EEG Device & 60000 & • & • & • & • \\ 
\hline 
Server & 4000 & • & • & • & • \\ 
\hline 
Workstations & Notebooks & 6400 & • & • & • & • \\ 
\hline 
\end{tabular}
\subsection{Material}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
Item & 1st Year & 2nd Year & 3rd Year & 4th Year & Sum \\ 
\hline 
Hardware for the Prototype & 2000 & • & • & • & 2000 \\ 
\hline 
EEG Sensors & 500 & • & • & • & 500 \\ 
\hline 
• & • & • & • & • & • \\ 
\hline 
\end{tabular} 
\subsection{Travel Costs}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
Item & 1st Year & 2nd Year & 3rd Year & 4th Year & Sum \\ 
\hline 
Conferences & 4000 & • & 4000 & • & 8000 \\ 
\hline 
EEG Sensors & 500 & • & • & • & 500 \\ 
\hline 
• & • & • & • & • & • \\ 
\hline 
\end{tabular} 
\subsection{Other Costs}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
Item & 1st Year & 2nd Year & 3rd Year & 4th Year & Sum \\ 
\hline 
Teambuilding, Snacks, Coffee, Meetings & 7000 & 7000 & 7000 & 3500 & 8000 \\
\hline 
\end{tabular}

### 2015-01-08 proposal/sections/ethics-security.tex
Costs

>>>>

\subsection{Ethical Considerations}
\begin{itemize}
\item {
At the moment there is an ongoing dispute in the public over weather or not long-term exposure to electromagnetic fields can cause cancer or changes in the brain chemistry. As far as we know today weak electromagnetic fields will have no effects on the human brain, but strong fields definitively do. The Wavy device will definitly create such a weak magnetic field (like all electric devices) and due to its location at the users ear and the intention of wearing it permanently it has the potential of harming the user if electromagnetic waves really have negative effects on the human brain. 
}
\item {
The Wavy device could be copied by companies trying to make a profit by constantly monitoring the emotional state of the user. The device would still function as an access device, but it could be misused for marketing purposes for example. A possible scenario could be: A company installs a wireless module into a TV set that sends a signal when an advertisment is shown. This signal activates an application in the user’s phone which in turn starts collecting emotional data via such a “bad” Wavy device from the user who is watching the advertisment. The company can then sell the gathered knowledge about the user’s response to the advertisment and his/her preferences to others such as the advertising company.
}
\end{itemize}

\subsection{Security Issues}
\begin{itemize}
\item{
At the current state of the technology mind reading is still science fiction, but basically a device such as the Wavy could be used to read all thoughts of a user. The only real issue that is preventing this scenario at the moment is that from a given set of brain waves there is currently no way of translating this user’s thought into a visual or textual representation for someone else to read. However, this may be possible at some point in the future. A compromised Wavy device poses a serious security risk for the user.
}
\item{
The biggest issue in security is probably the Bluetooth connection itself. We have to rely on the Bluethoot standard to be secure, as we cannot change it and there are basically no other alternatives to Bluetooth at the moment.
}
\item{
stromschlag bei regen??
}
\end{itemize}
